GVN-Hoist: Hoisting Computations from Branches

### 2016-08-24 hoist.tex
fix
related work

\author{
\alignauthor
Aditya Kumar\\
       \affaddr{Samsung Austin R\&D Center}\\
       \email{aditya.k7@samsung.com}
\alignauthor
Sebastian Pop\\
       \affaddr{Samsung Austin R\&D Center}\\
       \email{s.pop@samsung.com}
\and
\alignauthor
Daniel Berlin\\
       \affaddr{Google Inc.}\\
       \email{dberlin@dberlin.org}
}

@@

Rosen et al. explain moving computations successors to remove redundancies
\cite{rosen1988global}. Their algorithm iterates on computations of same rank
and move the code with identical computations from the sibling branch. This is a
pessimistic approach (TODO: is it?). Also there is no notion of partially
hoisting the computations so their approach may result is missing many hoisting
opportunities.

@@

@@

Currently, we rerun the algorithm until there are no more instructions left to
be hoisted. This is not the most optimal approach and results in expensive
analyses to be recomputed. This can be improved by ranking the computations
\cite{rosen1988global}.

>>>>

\author{
\alignauthor
Aditya Kumar\\
       \affaddr{Samsung Austin R\&D Center}\\
       \email{aditya.k7@samsung.com}
\alignauthor
Sebastian Pop\\
       \affaddr{Samsung Austin R\&D Center}\\
       \email{s.pop@samsung.com}
%\and
%\alignauthor
%Daniel Berlin\\
%       \affaddr{Google Inc.}\\
%       \email{dberlin@dberlin.org}
}

@@

Rosen et al. explain moving computations successors to remove redundancies
\cite{rosen1988global}. Their algorithm iterates on computations of same rank
and move the code with identical computations from the sibling branch. This is a
pessimistic approach (TODO: is it?). Also there is no notion of partially
hoisting the computations so their approach may result in missing many hoisting
opportunities.

@@

GCC implementation: Hoists top down in a predecessor where the value is in
ANTIC\_IN. This approach may have the problem of hoisting the expression too far
and to mititage that it only hoists expressions when at least one successor
computes it. Hence the algorithm will hoist a limited set of computations.  One
advantage of GCC implementation is that it works in sync with the GVN-PRE such
that when new hoisting opportunities are created by GVN-PRE, code-hoisting will
hoist them.

@@

Currently, we rerun the algorithm until there are no more instructions left to
be hoisted. This is not the most optimal approach and results in expensive
analyses to be recomputed. This can be improved by ranking the computations
\cite{rosen1988global}. Also gvn-hoist runs very early in the pass pipeline, it
will be good to evaluate the codesize/performance impact when it is run in sync
with gvn-pre just like gcc does.
